---
title: "detrend dome1"
author: "R Stern"
date: "July 5, 2017"
output: html_document
---

```{r}
library(dplR)
library(stats)
library(utils)
library(graphics)

choose.files()

#bring in dome1 RRW
dome1.rwl <- read.tucson( "C:\\Users\\Rebecca Stern\\Documents\\UVM\\Research\\QURU 2015-16\\QURU Sites\\Dome1\\QURU_Dome1.txt")
head(dome1.rwl)

#average multiple cores of same tree. first, try autoread.ids(file.rwl). If that doesn't work, then try stc.
dome1.ids.percore <- read.ids(dome1.rwl, stc = c(0,4,1))
dome1.ids.percore

dome1.treeMean <- treeMean(dome1.rwl, dome1.ids.percore)
tail(dome1.treeMean)

#Unlike other sites, 2015 was not removed from cores since trees were sampled in fall.
```

First, look at all possible detrending methods (methods offered by this function)
```{r}
detrend(dome1.treeMean, y.name = names(dome1.treeMean),  make.plot = TRUE, 
              method = c("Spline", "ModNegExp", "Mean","Ar", "Friedman"),
              nyrs = NULL, f = 0.5, pos.slope = FALSE, 
              constrain.modnegexp = c("never", "when.fail", "always"),
              verbose = TRUE, return.info = FALSE, span = "cv", bass = 0)
```

Detrend with a spline
```{r}
dome1.spline <- detrend(rwl = dome1.treeMean, method = "Spline")
tail(dome1.spline)

#check stats/EPS of spline method
#read in ids based on treeMean
dome1.ids.treeMean <- read.ids(dome1.treeMean,stc = c(0,4,1))
head(dome1.ids.treeMean)

dome1.stats.spline <- rwi.stats.running(dome1.spline, dome1.ids.treeMean,
                                            window.length = 10)
dome1.stats.spline 

#The "Spline" approach uses an spline where the frequency response is 0.50 at a wavelength of 0.67 * "series length in years", unless specified differently using nyrs and f in the function ffcsaps. This attempts to remove the low frequency variability that is due to biological or stand effects.

```

Create site chronology with spline (default spline settings):
```{r}
#When creating a mean chronology, if you choose "false" for prewhiten, then you will not get a residual chronology, only the standardized chronology. Prewhitening removes autocorrelation and produces a residual chronology.
dome1.spline.crn <- chron(dome1.spline, prefix = "DO1", 
                          biweight = TRUE, 
                          prewhiten = TRUE)
head(dome1.spline.crn)
tail(dome1.spline.crn)

#truncate based on EPS, which for this site was the year 1920- this is using the rownames values, not sure how to use the actual years (so rownames don't have to be counted...)
nrow(dome1.spline.crn)

dome1.spline.tcrn <- dome1.spline.crn [49:144,]
head(dome1.spline.tcrn)
tail(dome1.spline.tcrn)

par(mfrow=c(1,1))

plot(dome1.spline.tcrn,xlab="Year",ylab="RWI") #standardized chronology on top, residual chronology on bottom. Sample depth is trees, not cores.

#remove the standardized chronology to prep for creating CSV
dome1.spline.tcrn <-dome1.spline.tcrn[-1]
dome1.spline.tcrn <- cbind(rownames(dome1.spline.tcrn), dome1.spline.tcrn)
rownames(dome1.spline.tcrn) <- NULL
colnames(dome1.spline.tcrn) <- c("year","dome1_reschron","dome1.s.dep")
head(dome1.spline.tcrn)
tail(dome1.spline.tcrn)

#create CSV file for future reference (so don't have to re-run code every time)
write.csv(dome1.spline.tcrn, "C:\\Users\\Rebecca Stern\\Documents\\UVM\\Research\\QURU 2015-16\\QURU Sites\\Dome1\\QURU_dome1_defspline_trunc.csv", row.names=FALSE)

```

Detrend using 20-year spline:
```{r}
dome1.spline.20 <-detrend(dome1.treeMean, y.name = names(dome1.treeMean),  
              make.plot = FALSE, 
              method = "Spline",
              nyrs = 20, f = 0.5,
              verbose = FALSE, return.info = FALSE, span = "cv", bass = 0)

#check stats/EPS of 20-yr spline 
dome1.spline.20.stats  <- rwi.stats.running(dome1.spline.20, dome1.ids.treeMean,
                                            window.length = 10)
dome1.spline.20.stats
```

Create site chronology with 20-year spline:
```{r}
dome1.spline.20.crn <- chron(dome1.spline.20, prefix = "DO1", 
                          biweight = TRUE, 
                          prewhiten = TRUE)
head(dome1.spline.20.crn)
tail(dome1.spline.20.crn)

#truncate based on EPS, which for this site was the year 1920- this is using the rownames values, not sure how to use the actual years (so rownames don't have to be counted...)
nrow(dome1.spline.20.crn)

dome1.spline.20.tcrn <- dome1.spline.20.crn [49:144,]
head(dome1.spline.20.tcrn)
tail(dome1.spline.20.tcrn)

par(mfrow=c(1,1))

plot(dome1.spline.20.tcrn,xlab="Year",ylab="RWI") #standardized chronology on top, residual chronology on bottom. Sample depth is trees, not cores.

#remove the standardized chronology to prep for creating CSV
dome1.spline.20.tcrn <-dome1.spline.20.tcrn[-1]
dome1.spline.20.tcrn <- cbind(rownames(dome1.spline.20.tcrn), dome1.spline.20.tcrn)
rownames(dome1.spline.20.tcrn) <- NULL
colnames(dome1.spline.20.tcrn) <- c("year","dome1_reschron","dome1.s.dep")
head(dome1.spline.20.tcrn)
tail(dome1.spline.20.tcrn)

#create CSV file for future reference (so don't have to re-run code every time)
write.csv(dome1.spline.20.tcrn, "C:\\Users\\Rebecca Stern\\Documents\\UVM\\Research\\QURU 2015-16\\QURU Sites\\Dome1\\QURU_dome1_20spline_trunc.csv", row.names=FALSE)

```

Detrend using a 30 year spline
```{r}
dome1.spline.30 <- detrend(dome1.treeMean, y.name = names(dome1.treeMean),  
              make.plot = FALSE, 
              method = "Spline",
              nyrs = 30, f = 0.5,
              verbose = FALSE, return.info = FALSE, span = "cv", bass = 0)

#check stats/EPS of 30-yr spline 
dome1.spline.30.stats  <- rwi.stats.running(dome1.spline.30, dome1.ids.treeMean,
                                            window.length = 10)
dome1.spline.30.stats
```

Create site chronology with 30-year spline:
```{r}
dome1.spline.30.crn <- chron(dome1.spline.30, prefix = "DO1", 
                          biweight = TRUE, 
                          prewhiten = TRUE)
head(dome1.spline.30.crn)
tail(dome1.spline.30.crn)

#truncate based on EPS, which for this site was the year 1920- this is using the rownames values, not sure how to use the actual years (so rownames don't have to be counted...)
nrow(dome1.spline.30.crn)

dome1.spline.30.tcrn <- dome1.spline.30.crn [49:144,]
head(dome1.spline.30.tcrn)
tail(dome1.spline.30.tcrn)

par(mfrow=c(1,1))

plot(dome1.spline.30.tcrn,xlab="Year",ylab="RWI") #standardized chronology on top, residual chronology on bottom. Sample depth is trees, not cores.

#remove the standardized chronology to prep for creating CSV
dome1.spline.30.tcrn <-dome1.spline.30.tcrn[-1]
dome1.spline.30.tcrn <- cbind(rownames(dome1.spline.30.tcrn), dome1.spline.30.tcrn)
rownames(dome1.spline.30.tcrn) <- NULL
colnames(dome1.spline.30.tcrn) <- c("year","dome1_reschron","dome1.s.dep")
head(dome1.spline.30.tcrn)
tail(dome1.spline.30.tcrn)

#create CSV file for future reference (so don't have to re-run code every time)
write.csv(dome1.spline.30.tcrn, "C:\\Users\\Rebecca Stern\\Documents\\UVM\\Research\\QURU 2015-16\\QURU Sites\\Dome1\\QURU_dome1_30spline_trunc.csv", row.names=FALSE)
```

Detrend using a 40 year spline
```{r}
dome1.spline.40 <- detrend(dome1.treeMean, y.name = names(dome1.treeMean),  
              make.plot = FALSE, 
              method = "Spline",
              nyrs = 40, f = 0.5,
              verbose = FALSE, return.info = FALSE, span = "cv", bass = 0)

#check stats/EPS of 40-yr spline 
dome1.spline.40.stats  <- rwi.stats.running(dome1.spline.40, dome1.ids.treeMean,
                                            window.length = 10)
dome1.spline.40.stats
```


Create site chronology with 40-year spline:
```{r}
dome1.spline.40.crn <- chron(dome1.spline.40, prefix = "DO1", 
                          biweight = TRUE, 
                          prewhiten = TRUE)
head(dome1.spline.40.crn)
tail(dome1.spline.40.crn)

#truncate based on EPS, which for this site was the year 1920- this is using the rownames values, not sure how to use the actual years (so rownames don't have to be counted...)
nrow(dome1.spline.40.crn)

dome1.spline.40.tcrn <- dome1.spline.40.crn [49:144,]
head(dome1.spline.40.tcrn)
tail(dome1.spline.40.tcrn)

par(mfrow=c(1,1))

plot(dome1.spline.40.tcrn,xlab="Year",ylab="RWI") #standardized chronology on top, residual chronology on bottom. Sample depth is trees, not cores.

#remove the standardized chronology to prep for creating CSV
dome1.spline.40.tcrn <-dome1.spline.40.tcrn[-1]
dome1.spline.40.tcrn <- cbind(rownames(dome1.spline.40.tcrn), dome1.spline.40.tcrn)
rownames(dome1.spline.40.tcrn) <- NULL
colnames(dome1.spline.40.tcrn) <- c("year","dome1_reschron","dome1.s.dep")
head(dome1.spline.40.tcrn)
tail(dome1.spline.40.tcrn)

#create CSV file for future reference (so don't have to re-run code every time)
write.csv(dome1.spline.40.tcrn, "C:\\Users\\Rebecca Stern\\Documents\\UVM\\Research\\QURU 2015-16\\QURU Sites\\Dome1\\QURU_dome1_40spline_trunc.csv", row.names=FALSE)
```

Detrend using a 50 year spline
```{r}
dome1.spline.50 <- detrend(dome1.treeMean, y.name = names(dome1.treeMean),  
              make.plot = FALSE, 
              method = "Spline",
              nyrs = 50, f = 0.5,
              verbose = FALSE, return.info = FALSE, span = "cv", bass = 0)

#check stats/EPS of 50-yr spline 
dome1.spline.50.stats  <- rwi.stats.running(dome1.spline.50, dome1.ids.treeMean,
                                            window.length = 10)
dome1.spline.50.stats
```

Create site chronology with 50-year spline:
```{r}
dome1.spline.50.crn <- chron(dome1.spline.50, prefix = "DO1", 
                          biweight = TRUE, 
                          prewhiten = TRUE)
head(dome1.spline.50.crn)
tail(dome1.spline.50.crn)

#truncate based on EPS, which for this site was the year 1920- this is using the rownames values, not sure how to use the actual years (so rownames don't have to be counted...)
nrow(dome1.spline.50.crn)

dome1.spline.50.tcrn <- dome1.spline.50.crn [49:144,]
head(dome1.spline.50.tcrn)
tail(dome1.spline.50.tcrn)

par(mfrow=c(1,1))

plot(dome1.spline.50.tcrn,xlab="Year",ylab="RWI") #standardized chronology on top, residual chronology on bottom. Sample depth is trees, not cores.

#remove the standardized chronology to prep for creating CSV
dome1.spline.50.tcrn <-dome1.spline.50.tcrn[-1]
dome1.spline.50.tcrn <- cbind(rownames(dome1.spline.50.tcrn), dome1.spline.50.tcrn)
rownames(dome1.spline.50.tcrn) <- NULL
colnames(dome1.spline.50.tcrn) <- c("year","dome1_reschron","dome1.s.dep")
head(dome1.spline.50.tcrn)
tail(dome1.spline.50.tcrn)

#create CSV file for future reference (so don't have to re-run code every time)
write.csv(dome1.spline.50.tcrn, "C:\\Users\\Rebecca Stern\\Documents\\UVM\\Research\\QURU 2015-16\\QURU Sites\\Dome1\\QURU_dome1_50spline_trunc.csv", row.names=FALSE)
```


Detrend using FSS
```{r}
#detrend using FSS
dome1.fss <- detrend(rwl = dome1.treeMean, method = "Friedman")
tail(dome1.fss)

#check stats/EPS of FSS method
#read in ids based on treeMean
dome1.ids.treeMean <- read.ids(dome1.treeMean,stc = c(0,4,1))
head(dome1.ids.treeMean)

dome1.stats.fss <- rwi.stats.running(dome1.fss, dome1.ids.treeMean,
                                            window.length = 10)

dome1.stats.fss 
```

Create site chronology with FSS:
```{r}
dome1.fss.crn <- chron(dome1.fss, prefix = "DO1", 
                          biweight = TRUE, 
                          prewhiten = TRUE)
head(dome1.fss.crn)
tail(dome1.fss.crn)

#truncate based on EPS, which for this site was the year 1925:
nrow(dome1.fss.crn)

dome1.fss.tcrn <- dome1.fss.crn [54:144,]
head(dome1.fss.tcrn)
tail(dome1.fss.tcrn)

par(mfrow=c(1,1))

plot(dome1.fss.tcrn,xlab="Year",ylab="RWI") #standardized chronology on top, residual chronology on bottom. Sample depth is trees, not cores.

#remove the standardized chronology to prep for creating CSV
dome1.fss.tcrn <-dome1.fss.tcrn[-1]
dome1.fss.tcrn <- cbind(rownames(dome1.fss.tcrn), dome1.fss.tcrn)
rownames(dome1.fss.tcrn) <- NULL
colnames(dome1.fss.tcrn) <- c("year","dome1_reschron","dome1.s.dep")
head(dome1.fss.tcrn)
tail(dome1.fss.tcrn)

#create CSV file for future reference (so don't have to re-run code every time)
write.csv(dome1.fss.tcrn, "C:\\Users\\Rebecca Stern\\Documents\\UVM\\Research\\QURU 2015-16\\QURU Sites\\Dome1\\QURU_dome1_fss_trunc.csv", row.names=FALSE)
```

