---
title: "g-corrs elev RW"
author: "R Stern"
date: "April 13, 2018"
output: html_document
editor_options: 
  chunk_output_type: console
---

lower elev
```{r}
library(treeclim)
library(dplyr)

#setwd("C:\\Users\\Rebecca Stern\\Documents\\UVM\\Research\\QURU 2015-16")

choose.files()
low_elev.a<- read.csv( "C:\\Users\\Rebecca Stern\\Documents\\UVM\\Research\\QURU 2015-16\\Excel Files\\RW\\low_elev_sites_RWI.csv", header=T, row.names = 1)
head(low_elev.a)

low_elev <- select(low_elev.a, mean_low)
head(low_elev)

choose.files()
precip <- read.csv("C:\\Users\\Rebecca Stern\\Documents\\UVM\\Research\\QURU 2015-16\\Climate data\\mean_PRISM_ppt_quru.csv")
head (precip)

#stationary
#individual months
vt.quru.precip <- dcc(low_elev, precip, 
               selection = -6:9, method = "correlation",
               dynamic = "static", win_size = 25, win_offset = 1,
               start_last = TRUE, timespan = NULL, var_names = NULL, 
               ci = 0.05,
               boot = "std", sb = TRUE)

plot(vt.quru.precip)
coef(vt.quru.precip) # Jun (0.43), Jul(.39)

#moving
#individual months
vt.quru.precip2 <- dcc(low_elev, precip, 
                       selection = -6:9, method = "correlation",
                       dynamic = "moving", win_size = 25, win_offset = 1,
                       start_last = TRUE, var_names = NULL, ci = 0.05,
                       boot = "std", sb = TRUE)


summary(vt.quru.precip2)
plot(vt.quru.precip2)  
coef(vt.quru.precip2)

#stationary
#seasonal and water yr variables
vt.quru.precip3 <- dcc(low_elev, precip, 
               selection = .mean(-12:2) + .mean(3:5) 
               + .mean(6:8) + .mean (9:11) + .mean (-9:-11) 
               + .mean(-10:9) + .sum(-10:9),
               method = "correlation",
               dynamic = "static", win_size = 25, win_offset = 1,
               start_last = TRUE, timespan = NULL, var_names = NULL, 
               ci = 0.05,
               boot = "std", sb = TRUE)
plot(vt.quru.precip3)
coef(vt.quru.precip3) #summer(.39), fall (-.28)

#moving
#seasonal and wyr
vt.quru.precip4 <- dcc(low_elev, precip,selection = .mean(-12:2) 
                       + .mean(3:5) + .mean(6:8)+ .mean (9:11) + .mean (-9:-11)+ .mean(-10:9) 
                       + .sum(-10:9), 
                       method = "correlation",dynamic = "moving", win_size = 25, 
                       win_offset = 1, start_last = TRUE, var_names = NULL, ci = 0.05,
                       boot = "std", sb = TRUE)

plot(vt.quru.precip4)  
coef(vt.quru.precip4)


##tmin
choose.files()

tmin <- read.csv("C:\\Users\\Rebecca Stern\\Documents\\UVM\\Research\\QURU 2015-16\\Climate data\\mean_PRISM_tmin_quru.csv")
head (tmin)

#stationary
#individual months
vt.quru.tmin <- dcc(low_elev, tmin, selection = -6:9, method = "correlation",
                    dynamic = "static", win_size = 25, win_offset = 1,
                    start_last = TRUE, timespan = NULL, var_names = NULL, 
                    ci = 0.05,
                    boot = "std", sb = TRUE)

plot(vt.quru.tmin) 
coef(vt.quru.tmin) #Oct (.25)

#moving
vt.quru.tmin2 <- dcc(low_elev, tmin, selection = -6:9, method = "correlation",
                    dynamic = "moving", win_size = 25, win_offset = 1,
                    start_last = TRUE, timespan = NULL, var_names = NULL, 
                    ci = 0.05,
                    boot = "std", sb = TRUE)

plot(vt.quru.tmin2) 

#stationary
#seasonal and Wyr 
vt.quru.tmin3 <- dcc(low_elev, tmin, selection = .mean(-12:2) 
                       + .mean(3:5) + .mean(6:8)
                       + .mean (9:11) + .mean (-9:-11) + .mean(-10:9) 
                     + .sum(-10:9), method = "correlation",
                    dynamic = "static", win_size = 25, win_offset = 1,
                    start_last = TRUE, timespan = NULL, var_names = NULL, 
                    ci = 0.05, boot = "std", sb = TRUE)

plot(vt.quru.tmin3) #none sig

#moving
#seasonal and Wyr 
vt.quru.tmin4 <- dcc(low_elev, tmin, selection = .mean(-12:2) 
                       + .mean(3:5) + .mean(6:8)
                       + .mean (9:11) + .mean (-9:-11) + .mean(-10:9) 
                     + .sum(-10:9), method = "correlation",
                    dynamic = "moving", win_size = 25, win_offset = 1,
                    start_last = TRUE, timespan = NULL, var_names = NULL, 
                    ci = 0.05, boot = "std", sb = TRUE)

plot(vt.quru.tmin4) 

##tmean
choose.files()
tmean <- read.csv("C:\\Users\\Rebecca Stern\\Documents\\UVM\\Research\\QURU 2015-16\\Climate data\\mean_PRISM_tmean_quru.csv")
head (tmean)

#stationary
#inidividual months
vt.quru.tmean<- dcc(low_elev, tmean,selection = -6:9, method = "correlation",
                       dynamic = "static", win_size = 25, win_offset = 1,
                    start_last = TRUE, timespan = NULL, var_names = NULL, 
                    ci = 0.05, boot = "std", sb = TRUE)

plot(vt.quru.tmean) 
coef(vt.quru.tmean) # oct (.27), Jun(-.24)

#moving
vt.quru.tmean2 <- dcc(low_elev, tmean, selection = -6:9, method ="correlation",
                       dynamic = "moving", win_size = 25, win_offset = 1,
                    start_last = TRUE, timespan = NULL, var_names = NULL, 
                    ci = 0.05, boot = "std", sb = TRUE)

plot(vt.quru.tmean2) 
coef(vt.quru.tmean2) 

#static
#seasonal, Wyr
vt.quru.tmean3 <- dcc(low_elev, tmean,selection = .mean(-12:2) 
                       + .mean(3:5) + .mean(6:8) + .mean (9:11) + .mean (-9:-11) 
                      + .mean(-10:9)  + .sum(-10:9), method = "correlation",
                       dynamic = "static", win_size = 25, win_offset = 1,
                    start_last = TRUE, timespan = NULL, var_names = NULL, ci = 0.05,
                    boot = "std", sb = TRUE)

plot(vt.quru.tmean3) #none sig
coef(vt.quru.tmean3) 

#moving
#seasonal and Wyr
vt.quru.tmean4<- dcc(low_elev, tmean,selection =  .mean(-12:2) 
                       + .mean(3:5) + .mean(6:8)
                       + .mean (9:11) + .mean (-9:-11), method = "correlation",
                       dynamic = "static", win_size = 25, win_offset = 1,
                    start_last = TRUE, timespan = NULL, var_names = NULL, ci = 0.05,
                    boot = "std", sb = TRUE)

plot(vt.quru.tmean4) 
coef(vt.quru.tmean4) 

##tmax
choose.files()
tmax <- read.csv("C:\\Users\\Rebecca Stern\\Documents\\UVM\\Research\\QURU 2015-16\\Climate data\\mean_PRISM_tmax_quru.csv")
head (tmax)

#Correlation function analysis (stationary):
#individual months
vt.quru.tmax <- dcc(low_elev, tmax, 
               selection = -6:9, method = "correlation",
               dynamic = "static", win_size = 25, win_offset = 1,
               start_last = TRUE, timespan = NULL, var_names = NULL, 
               ci = 0.05,
               boot = "std", sb = TRUE)

plot(vt.quru.tmax)
coef(vt.quru.tmax) #pJun(.26), Jun(-.35)

#moving
#individual months
vt.quru.tmax2 <- dcc(low_elev, tmax, 
                       selection = -6:9, method = "correlation",
                       dynamic = "moving", win_size = 25, win_offset = 1,
                       start_last = TRUE, var_names = NULL, ci = 0.05,
                       boot = "std", sb = TRUE)
plot(vt.quru.tmax2)  
coef(vt.quru.tmax2)

#seasonal and water yr variables
vt.quru.tmax3 <- dcc(low_elev, tmax, 
               selection = .mean(-12:2) + .mean(3:5) 
               + .mean(6:8) + .mean (9:11) + .mean (-9:-11) 
               + .mean(-10:9) + .sum(-10:9),
               method = "correlation",
               dynamic = "static", win_size = 25, win_offset = 1,
               start_last = TRUE, timespan = NULL, var_names = NULL, 
               ci = 0.05,
               boot = "std", sb = TRUE)
plot(vt.quru.tmax3)
coef(vt.quru.tmax3) #summer(-.26)

#seasonal and wyr
vt.quru.tmax4 <- dcc(low_elev, tmax, 
                       selection = .mean(-12:2) 
                       + .mean(3:5) + .mean(6:8)
                       + .mean (9:11) + .mean (-9:-11)+ .mean(-10:9) 
                       + .sum(-10:9), 
                       method = "correlation",
                       dynamic = "moving", win_size = 25, 
                       win_offset = 1,
                       start_last = TRUE, var_names = NULL, ci = 0.05,
                       boot = "std", sb = TRUE)
plot(vt.quru.tmax4)  
coef(vt.quru.tmax4)

##SPEI
choose.files()
spei_01 <- read.csv("C:\\Users\\Rebecca Stern\\Documents\\UVM\\Research\\QURU 2015-16\\Climate data\\mean_spei_01.csv")
head (spei_01)

vt.quru.spei.01 <- dcc(low_elev, spei_01, selection = -6:9, 
                       method =  "correlation",
                  dynamic = "static", win_size = 25, win_offset = 1,
                 start_last = TRUE, timespan = NULL, var_names = NULL, 
                 ci = 0.05,
                 boot = "std", sb = TRUE)

plot(vt.quru.spei.01) #Jun(.42), Jul(.38)
coef(vt.quru.spei.01)

#SPEI03
spei_03 <- read.csv("C:\\Users\\Rebecca Stern\\Documents\\UVM\\Research\\QURU 2015-16\\Climate data\\mean_spei_03.csv")
head (spei_03)

vt.quru.spei.03 <- dcc(low_elev, spei_03, selection = -6:9, 
                       method =  "correlation", dynamic = "static",
                       win_size = 25, win_offset = 1, 
                       start_last = TRUE,  var_names = NULL, 
                        ci = 0.05, boot = "std", sb = TRUE)

plot(vt.quru.spei.03) 
coef(vt.quru.spei.03) #pJun(-.24), Jun(.34), JUl(.46), Aug(.36)

#SPEI06
spei_06 <- read.csv("C:\\Users\\Rebecca Stern\\Documents\\UVM\\Research\\QURU 2015-16\\Climate data\\mean_spei_06.csv")
head(spei_06)

vt.quru.spei.06 <- dcc(low_elev, spei_06, selection = -6:9, 
                       method =    "correlation",
                  dynamic = "static", win_size = 25, win_offset = 1,
                 start_last = TRUE, timespan = NULL, var_names = NULL, 
                 ci = 0.05,
                 boot = "std", sb = TRUE)

plot(vt.quru.spei.06) 
coef(vt.quru.spei.06) #pJun(-.23), pDec(.22), Jan(.22), Jun(.23), Jul(.33), Aug(.31), Sep.(.26)

#SPEI09
choose.files()
spei_09 <- read.csv("C:\\Users\\Rebecca Stern\\Documents\\UVM\\Research\\QURU 2015-16\\Climate data\\mean_spei_09.csv")
head(spei_09)

vt.quru.spei.09 <- dcc(low_elev, spei_09, selection = -9:9, 
                       method =    "correlation",
                  dynamic = "static", win_size = 25, win_offset = 1,
                 start_last = TRUE, timespan = NULL, var_names = NULL, 
                 ci = 0.05,
                 boot = "std", sb = TRUE)

plot(vt.quru.spei.09) 
coef(vt.quru.spei.09) #Jul(.32), Aug(.24)


##PDSI
choose.files()
pdsi <- read.csv("C:\\Users\\Rebecca Stern\\Documents\\UVM\\Research\\QURU 2015-16\\Climate data\\PDSI VT Division 2.csv")
head(pdsi)

#static
vt.quru.pdsi <- dcc(low_elev, pdsi, selection = -6:9, 
                       method =    "correlation", dynamic = "static",
                       win_size = 25, win_offset = 1,
                       start_last = TRUE, timespan = NULL, 
                       var_names = NULL, ci = 0.05, boot = "std", 
                    sb = TRUE)

plot(vt.quru.pdsi) 
coef(vt.quru.pdsi) #Jun(.31), Jul(.38), Aug(.28)

#moving
vt.quru.pdsi2 <- dcc(low_elev, pdsi, selection = -6:9, 
                       method =    "correlation", dynamic = "moving",
                       win_size = 25, win_offset = 1,
                       start_last = TRUE, timespan = NULL, 
                       var_names = NULL, ci = 0.05, boot = "std", 
                    sb = TRUE)

plot(vt.quru.pdsi2) 
coef(vt.quru.pdsi2)

#HDD
choose.files()
hdd <- read.csv( "C:\\Users\\Rebecca Stern\\Documents\\UVM\\Research\\QURU 2015-16\\Climate data\\HDD VT Division 2.csv")
head(hdd)

#static
vt.quru.hdd <- dcc(low_elev, hdd, selection = -6:9,
                       method =    "correlation", 
                   dynamic = "static",
                       win_size = 25, win_offset = 1,
                       start_last = TRUE, timespan = NULL, 
                       var_names = NULL, ci = 0.05, boot = "std", 
                    sb = TRUE)

plot(vt.quru.hdd) 
coef(vt.quru.hdd) #pJun(-.22), pOct(-.28), Jun(.24)

#moving
vt.quru.hdd2 <- dcc(low_elev, hdd, selection = -6:9, 
                       method =    "correlation", dynamic = "moving",
                       win_size = 25, win_offset = 1,
                       start_last = TRUE, timespan = NULL, 
                       var_names = NULL, ci = 0.05, boot = "std", 
                    sb = TRUE)

plot(vt.quru.hdd2) 
coef(vt.quru.hdd2)


#CDD
choose.files()
cdd <- read.csv("C:\\Users\\Rebecca Stern\\Documents\\UVM\\Research\\QURU 2015-16\\Climate data\\CDD VT Division 2.csv")
head(cdd)
tail(cdd)

#static
vt.quru.cdd <- dcc(low_elev, cdd, selection = .range(-5:-9) + .range(5:9) + .mean(6:8) + .sum(6:8), 
                       method =  "correlation", 
                       dynamic = "static",
                       win_size = 25, win_offset = 1,
                       start_last = TRUE, timespan = NULL, 
                       var_names = NULL, ci = 0.05, boot = "std", sb = TRUE)

plot(vt.quru.cdd) 
coef(vt.quru.cdd) #none sig

#moving- error here
vt.quru.cdd2 <- dcc(low_elev, cdd, selection = .range(-6:-9) + .range(6:9), 
                       method = "correlation", dynamic = "moving",
                       win_size = 25, win_offset = 1,
                       start_last = TRUE, timespan = NULL, 
                       var_names = NULL, ci = 0.05, boot = "std", 
                    sb = TRUE)

plot(vt.quru.cdd2) 
coef(vt.quru.cdd2)

##NADP
choose.files()
nadp <- read.csv("C:\\Users\\Rebecca Stern\\Documents\\UVM\\Research\\Climate, Dep Data\\NADP\\mean NADP all vars.csv")
head(nadp)
tail(nadp)

#individual months, prev year (-6:-12)
vt.quru.nadp <- dcc(low_elev, nadp, 
               selection = -6:-12, method = "correlation",
               dynamic = "static", win_size = 25, win_offset = 1,
               start_last = TRUE, timespan = NULL, var_names = NULL, 
               ci = 0.05,
               boot = "std", sb = TRUE)

plot(vt.quru.nadp)
coef(vt.quru.nadp) #NO3 pJun(-.41), NO3 pDec(-.32), SO4 pJun(-.37), SO4 pDec(-.29)

#individual months, current year winter spring (1:6)
vt.quru.nadp2 <- dcc(low_elev, nadp, 
               selection = 1:6, method = "correlation",
               dynamic = "static", win_size = 25, win_offset = 1,
               start_last = TRUE, timespan = NULL, var_names = NULL, 
               ci = 0.05,
               boot = "std", sb = TRUE)

plot(vt.quru.nadp2)
coef(vt.quru.nadp2)# NO3 Apr(-.26), c.a.ratio Jan(.32), SO4 Feb (-.34)

#individual months, current year summer fall (7:10)
vt.quru.nadp3 <- dcc(low_elev, nadp, 
               selection = 7:10, method = "correlation",
               dynamic = "static", win_size = 25, win_offset = 1,
               start_last = TRUE, timespan = NULL, var_names = NULL, 
               ci = 0.05,
               boot = "std", sb = TRUE)

plot(vt.quru.nadp3)
coef(vt.quru.nadp3) # NO3 Jul(-.25), c.a.ratio Jul (-.31)

#water year mean and sum
vt.quru.nadp4 <- dcc(low_elev, nadp,  selection = .mean(-10:9) +.sum(-10:9), 
                       method = "correlation",
                       dynamic = "static", win_size = 25, win_offset = 1,
                       start_last = TRUE, var_names = NULL, ci = 0.05,
                       boot = "std", sb = TRUE)

plot(vt.quru.nadp4) 
coef(vt.quru.nadp4) #NO3 Wyr mean and sum(-.29), SO4 Wyr mean and sum(-.49)

#seasonal 
vt.quru.nadp5 <- dcc(low_elev, nadp,  selection = .mean(-12:2) 
                       + .mean(3:5) + .mean(6:8) + .mean (9:11) + .mean (-9:-11), 
                       method = "correlation",
                       dynamic = "static", win_size = 25, win_offset = 1,
                       start_last = TRUE, var_names = NULL, ci = 0.05,
                       boot = "std", sb = TRUE)

plot(vt.quru.nadp5) 
coef(vt.quru.nadp5) #NO3 winter(-.35), SO4 winter (-.34)

##CO2
choose.files()
quru.co2.low_elev  <- read.csv( "C:\\Users\\Rebecca Stern\\Documents\\UVM\\Research\\QURU 2015-16\\Excel Files\\RW\\co2_low_elev_quru.csv")
head(quru.co2.low_elev)

qx <- quru.co2.low_elev$mean_low
qy <- quru.co2.low_elev$mean_CO2

#Correlation:
cor.test(qx,qy, method = "pearson", data=quru.co2.low_elev, na.omit=TRUE) #ns, results below
```
Pearson's product-moment correlation

data:  qx and qy
t = 0.27092, df = 78, p-value = 0.7872
alternative hypothesis: true correlation is not equal to 0
95 percent confidence interval:
 -0.1903382  0.2487024
sample estimates:
       cor 
0.03066096 

Higher elev
```{r}
library(treeclim)

#setwd("C:\\Users\\Rebecca Stern\\Documents\\UVM\\Research\\QURU 2015-16")

choose.files()
high_elev.a<- read.csv("C:\\Users\\Rebecca Stern\\Documents\\UVM\\Research\\QURU 2015-16\\Excel Files\\RW\\high_elev_sites_RWI.csv", header=T, row.names = 1)
head(high_elev.a)

high_elev <- select(high_elev.a, mean_high)
head(high_elev)

choose.files()
precip <- read.csv("C:\\Users\\Rebecca Stern\\Documents\\UVM\\Research\\QURU 2015-16\\Climate data\\mean_PRISM_ppt_quru.csv")
head (precip)

#stationary
#individual months
vt.h.e.precip <- dcc(high_elev, precip, 
               selection = -6:9, method = "correlation",
               dynamic = "static", win_size = 25, win_offset = 1,
               start_last = TRUE, timespan = NULL, var_names = NULL, 
               ci = 0.05,
               boot = "std", sb = TRUE)

plot(vt.h.e.precip)
coef(vt.h.e.precip) # pSep(.23), Jun(.33), Jul(.34)

#moving
#individual months
vt.h.e.precip2 <- dcc(high_elev, precip, 
                       selection = -6:9, method = "correlation",
                       dynamic = "moving", win_size = 25, win_offset = 1,
                       start_last = TRUE, var_names = NULL, ci = 0.05,
                       boot = "std", sb = TRUE)


summary(vt.h.e.precip2)
plot(vt.h.e.precip2)  
coef(vt.h.e.precip2)

#stationary
#seasonal and water yr variables
vt.h.e.precip3 <- dcc(high_elev, precip, 
               selection = .mean(-12:2) + .mean(3:5) 
               + .mean(6:8) + .mean (9:11) + .mean (-9:-11) 
               + .mean(-10:9) + .sum(-10:9),
               method = "correlation",
               dynamic = "static", win_size = 25, win_offset = 1,
               start_last = TRUE, timespan = NULL, var_names = NULL, 
               ci = 0.05,
               boot = "std", sb = TRUE)
plot(vt.h.e.precip3)
coef(vt.h.e.precip3) #summer(.37)

#moving
#seasonal and wyr
vt.h.e.precip4 <- dcc(high_elev, precip,selection = .mean(-12:2) 
                       + .mean(3:5) + .mean(6:8)+ .mean (9:11) + .mean (-9:-11)+ .mean(-10:9) 
                       + .sum(-10:9), 
                       method = "correlation",dynamic = "moving", win_size = 25, 
                       win_offset = 1, start_last = TRUE, var_names = NULL, ci = 0.05,
                       boot = "std", sb = TRUE)

plot(vt.h.e.precip4)  
coef(vt.h.e.precip4)


##tmin
choose.files()

tmin <- read.csv("C:\\Users\\Rebecca Stern\\Documents\\UVM\\Research\\QURU 2015-16\\Climate data\\mean_PRISM_tmin_quru.csv")
head (tmin)

#stationary
#individual months
vt.h.e.tmin <- dcc(high_elev, tmin, selection = -6:9, method = "correlation",
                    dynamic = "static", win_size = 25, win_offset = 1,
                    start_last = TRUE, timespan = NULL, var_names = NULL, 
                    ci = 0.05,
                    boot = "std", sb = TRUE)

plot(vt.h.e.tmin) #Aug(.28)
coef(vt.h.e.tmin)

#moving
vt.h.e.tmin2 <- dcc(high_elev, tmin, selection = -6:9, method = "correlation",
                    dynamic = "moving", win_size = 25, win_offset = 1,
                    start_last = TRUE, timespan = NULL, var_names = NULL, 
                    ci = 0.05,
                    boot = "std", sb = TRUE)

plot(vt.h.e.tmin2) 

#stationary
#seasonal and Wyr 
vt.h.e.tmin3 <- dcc(high_elev, tmin, selection = .mean(-12:2) 
                       + .mean(3:5) + .mean(6:8)
                       + .mean (9:11) + .mean (-9:-11) + .mean(-10:9) 
                     + .sum(-10:9), method = "correlation",
                    dynamic = "static", win_size = 25, win_offset = 1,
                    start_last = TRUE, timespan = NULL, var_names = NULL, 
                    ci = 0.05, boot = "std", sb = TRUE)

plot(vt.h.e.tmin3) #NS

#moving
#seasonal and Wyr 
vt.h.e.tmin4 <- dcc(high_elev, tmin, selection = .mean(-12:2) 
                       + .mean(3:5) + .mean(6:8)
                       + .mean (9:11) + .mean (-9:-11) + .mean(-10:9) 
                     + .sum(-10:9), method = "correlation",
                    dynamic = "moving", win_size = 25, win_offset = 1,
                    start_last = TRUE, timespan = NULL, var_names = NULL, 
                    ci = 0.05, boot = "std", sb = TRUE)

plot(vt.h.e.tmin4) 

##tmean
choose.files()
tmean <- read.csv("C:\\Users\\Rebecca Stern\\Documents\\UVM\\Research\\QURU 2015-16\\Climate data\\mean_PRISM_tmean_quru.csv")
head (tmean)

#stationary
#inidividual months
vt.h.e.tmean<- dcc(high_elev, tmean,selection = -6:9, method = "correlation",
                       dynamic = "static", win_size = 25, win_offset = 1,
                    start_last = TRUE, timespan = NULL, var_names = NULL, 
                    ci = 0.05, boot = "std", sb = TRUE)

plot(vt.h.e.tmean) 
coef(vt.h.e.tmean) #Jun(-.25), Aug(.25)

#moving
vt.h.e.tmean2 <- dcc(high_elev, tmean, selection = -6:9, method ="correlation",
                       dynamic = "moving", win_size = 25, win_offset = 1,
                    start_last = TRUE, timespan = NULL, var_names = NULL, 
                    ci = 0.05, boot = "std", sb = TRUE)

plot(vt.h.e.tmean2) 
coef(vt.h.e.tmean2) 

#static
#seasonal, Wyr
vt.h.e.tmean3 <- dcc(high_elev, tmean,selection = .mean(-12:2) 
                       + .mean(3:5) + .mean(6:8) + .mean (9:11) + .mean (-9:-11) 
                      + .mean(-10:9)  + .sum(-10:9), method = "correlation",
                       dynamic = "static", win_size = 25, win_offset = 1,
                    start_last = TRUE, timespan = NULL, var_names = NULL, ci = 0.05,
                    boot = "std", sb = TRUE)

plot(vt.h.e.tmean3) #NS
coef(vt.h.e.tmean3) 

#moving
#seasonal and Wyr
vt.h.e.tmean4<- dcc(high_elev, tmean,selection =  .mean(-12:2) 
                       + .mean(3:5) + .mean(6:8)
                       + .mean (9:11) + .mean (-9:-11), method = "correlation",
                       dynamic = "static", win_size = 25, win_offset = 1,
                    start_last = TRUE, timespan = NULL, var_names = NULL, ci = 0.05,
                    boot = "std", sb = TRUE)

plot(vt.h.e.tmean4) 
coef(vt.h.e.tmean4) 

##tmax
choose.files()
tmax <- read.csv("C:\\Users\\Rebecca Stern\\Documents\\UVM\\Research\\QURU 2015-16\\Climate data\\mean_PRISM_tmax_quru.csv")
head (tmax)

#Correlation function analysis (stationary):
#individual months
vt.h.e.tmax <- dcc(high_elev, tmax, 
               selection = -6:9, method = "correlation",
               dynamic = "static", win_size = 25, win_offset = 1,
               start_last = TRUE, timespan = NULL, var_names = NULL, 
               ci = 0.05,
               boot = "std", sb = TRUE)

plot(vt.h.e.tmax)
coef(vt.h.e.tmax) #Jun(-.36)

#moving
#individual months
vt.h.e.tmax2 <- dcc(high_elev, tmax, 
                       selection = -6:9, method = "correlation",
                       dynamic = "moving", win_size = 25, win_offset = 1,
                       start_last = TRUE, var_names = NULL, ci = 0.05,
                       boot = "std", sb = TRUE)
plot(vt.h.e.tmax2)  
coef(vt.h.e.tmax2)

#seasonal and water yr variables
vt.h.e.tmax3 <- dcc(high_elev, tmax, 
               selection = .mean(-12:2) + .mean(3:5) 
               + .mean(6:8) + .mean (9:11) + .mean (-9:-11) 
               + .mean(-10:9) + .sum(-10:9),
               method = "correlation",
               dynamic = "static", win_size = 25, win_offset = 1,
               start_last = TRUE, timespan = NULL, var_names = NULL, 
               ci = 0.05,
               boot = "std", sb = TRUE)
plot(vt.h.e.tmax3)
coef(vt.h.e.tmax3) #NS

#seasonal and wyr
vt.h.e.tmax4 <- dcc(high_elev, tmax, 
                       selection = .mean(-12:2) 
                       + .mean(3:5) + .mean(6:8)
                       + .mean (9:11) + .mean (-9:-11)+ .mean(-10:9) 
                       + .sum(-10:9), 
                       method = "correlation",
                       dynamic = "moving", win_size = 25, 
                       win_offset = 1,
                       start_last = TRUE, var_names = NULL, ci = 0.05,
                       boot = "std", sb = TRUE)
plot(vt.h.e.tmax4)  
coef(vt.h.e.tmax4)

##SPEI
choose.files()
spei_01 <- read.csv("C:\\Users\\Rebecca Stern\\Documents\\UVM\\Research\\QURU 2015-16\\Climate data\\mean_spei_01.csv")
head (spei_01)

vt.h.e.spei.01 <- dcc(high_elev, spei_01, selection = -6:9, 
                       method =  "correlation",
                  dynamic = "static", win_size = 25, win_offset = 1,
                 start_last = TRUE, timespan = NULL, var_names = NULL, 
                 ci = 0.05,
                 boot = "std", sb = TRUE)

plot(vt.h.e.spei.01) #pSep(.25), Jun(.34), Jul (.25)
coef(vt.h.e.spei.01)

#SPEI03
spei_03 <- read.csv("C:\\Users\\Rebecca Stern\\Documents\\UVM\\Research\\QURU 2015-16\\Climate data\\mean_spei_03.csv")
head (spei_03)

vt.h.e.spei.03 <- dcc(high_elev, spei_03, selection = -6:9, 
                       method =  "correlation", dynamic = "static",
                       win_size = 25, win_offset = 1, 
                       start_last = TRUE,  var_names = NULL, 
                        ci = 0.05, boot = "std", sb = TRUE)

plot(vt.h.e.spei.03) #pSep(.27), Jun(.26), Jul(.28)
coef(vt.h.e.spei.03)

#SPEI06
spei_06 <- read.csv("C:\\Users\\Rebecca Stern\\Documents\\UVM\\Research\\QURU 2015-16\\Climate data\\mean_spei_06.csv")
head(spei_06)

vt.h.e.spei.06 <- dcc(high_elev, spei_06, selection = -6:9, 
                       method =    "correlation",
                  dynamic = "static", win_size = 25, win_offset = 1,
                 start_last = TRUE, timespan = NULL, var_names = NULL, 
                 ci = 0.05,
                 boot = "std", sb = TRUE)

plot(vt.h.e.spei.06) #pDec(.23), Jan(.23), Jul(.24), Aug(.24), Sep(.22)
coef(vt.h.e.spei.06)

#SPEI09
choose.files()
spei_09 <- read.csv("C:\\Users\\Rebecca Stern\\Documents\\UVM\\Research\\QURU 2015-16\\Climate data\\mean_spei_09.csv")
head(spei_09)

vt.h.e.spei.09 <- dcc(high_elev, spei_09, selection = -9:9, 
                       method =    "correlation",
                  dynamic = "static", win_size = 25, win_offset = 1,
                 start_last = TRUE, timespan = NULL, var_names = NULL, 
                 ci = 0.05,
                 boot = "std", sb = TRUE)

plot(vt.h.e.spei.09) #Jul(.24)
coef(vt.h.e.spei.09)


##PDSI
choose.files()
pdsi <- read.csv("C:\\Users\\Rebecca Stern\\Documents\\UVM\\Research\\QURU 2015-16\\Climate data\\PDSI VT Division 2.csv")
head(pdsi)

#static
vt.h.e.pdsi <- dcc(high_elev, pdsi, selection = -6:9, 
                       method =    "correlation", dynamic = "static",
                       win_size = 25, win_offset = 1,
                       start_last = TRUE, timespan = NULL, 
                       var_names = NULL, ci = 0.05, boot = "std", 
                    sb = TRUE)

plot(vt.h.e.pdsi) 
coef(vt.h.e.pdsi)#Jun(.27), Jul(.33), Aug(.26), Sep(.23)

#moving
vt.h.e.pdsi2 <- dcc(high_elev, pdsi, selection = -6:9, 
                       method =    "correlation", dynamic = "moving",
                       win_size = 25, win_offset = 1,
                       start_last = TRUE, timespan = NULL, 
                       var_names = NULL, ci = 0.05, boot = "std", 
                    sb = TRUE)

plot(vt.h.e.pdsi2) 
coef(vt.h.e.pdsi2)

#HDD
choose.files()
hdd <- read.csv( "C:\\Users\\Rebecca Stern\\Documents\\UVM\\Research\\QURU 2015-16\\Climate data\\HDD VT Division 2.csv")
head(hdd)

#static
vt.h.e.hdd <- dcc(high_elev, hdd, selection = -6:9,
                       method =    "correlation", 
                   dynamic = "static",
                       win_size = 25, win_offset = 1,
                       start_last = TRUE, timespan = NULL, 
                       var_names = NULL, ci = 0.05, boot = "std", 
                    sb = TRUE)

plot(vt.h.e.hdd) 
coef(vt.h.e.hdd) #Jun(.25), Aug(-.24)

#moving
vt.h.e.hdd2 <- dcc(high_elev, hdd, selection = -6:9, 
                       method =    "correlation", dynamic = "moving",
                       win_size = 25, win_offset = 1,
                       start_last = TRUE, timespan = NULL, 
                       var_names = NULL, ci = 0.05, boot = "std", 
                    sb = TRUE)

plot(vt.h.e.hdd2) 
coef(vt.h.e.hdd2)


#CDD
choose.files()
cdd <- read.csv("C:\\Users\\Rebecca Stern\\Documents\\UVM\\Research\\QURU 2015-16\\Climate data\\CDD VT Division 2.csv")
head(cdd)
tail(cdd)

#static
vt.h.e.cdd <- dcc(high_elev, cdd, selection = .range(-5:-9) + .range(5:9) + .mean(6:8) + .sum(6:8), 
                       method =  "correlation", 
                       dynamic = "static",
                       win_size = 25, win_offset = 1,
                       start_last = TRUE, timespan = NULL, 
                       var_names = NULL, ci = 0.05, boot = "std", sb = TRUE)

plot(vt.h.e.cdd) 
coef(vt.h.e.cdd) #Jun(-.27), Aug(.26)

#moving- error here
vt.h.e.cdd2 <- dcc(high_elev, cdd, selection = .range(-6:-9) + .range(6:9), 
                       method = "correlation", dynamic = "moving",
                       win_size = 25, win_offset = 1,
                       start_last = TRUE, timespan = NULL, 
                       var_names = NULL, ci = 0.05, boot = "std", 
                    sb = TRUE)

plot(vt.h.e.cdd2) 
coef(vt.h.e.cdd2)

##NADP
choose.files()
nadp <- read.csv("C:\\Users\\Rebecca Stern\\Documents\\UVM\\Research\\Climate, Dep Data\\NADP\\mean NADP all vars.csv")
head(nadp)
tail(nadp)

plot(Mean_Ratio_c.a ~Year, data= nadp)

plot(Mean_NO3 ~Year, data= nadp)

#individual months, prev year (-6:-12)
vt.h.e.nadp <- dcc(high_elev, nadp, 
               selection = -6:-12, method = "correlation",
               dynamic = "static", win_size = 25, win_offset = 1,
               start_last = TRUE, timespan = NULL, var_names = NULL, 
               ci = 0.05,
               boot = "std", sb = TRUE)

plot(vt.h.e.nadp)
coef(vt.h.e.nadp) #SO4 pAug(-.34), SO4 pNov(-.28)

#individual months, current year winter spring (1:6)
vt.h.e.nadp2 <- dcc(high_elev, nadp, 
               selection = 1:6, method = "correlation",
               dynamic = "static", win_size = 25, win_offset = 1,
               start_last = TRUE, timespan = NULL, var_names = NULL, 
               ci = 0.05,
               boot = "std", sb = TRUE)

plot(vt.h.e.nadp2)
coef(vt.h.e.nadp2) #NS

#individual months, current year summer fall (7:10)
vt.h.e.nadp3 <- dcc(high_elev, nadp, 
               selection = 7:10, method = "correlation",
               dynamic = "static", win_size = 25, win_offset = 1,
               start_last = TRUE, timespan = NULL, var_names = NULL, 
               ci = 0.05,
               boot = "std", sb = TRUE)

plot(vt.h.e.nadp3)
coef(vt.h.e.nadp3) #NS

#water year mean and sum
vt.h.e.nadp4 <- dcc(high_elev, nadp,  selection = .mean(-10:9) +.sum(-10:9), 
                       method = "correlation",
                       dynamic = "static", win_size = 25, win_offset = 1,
                       start_last = TRUE, var_names = NULL, ci = 0.05,
                       boot = "std", sb = TRUE)

plot(vt.h.e.nadp4) 
coef(vt.h.e.nadp4) #NS

#seasonal 
vt.h.e.nadp5 <- dcc(high_elev, nadp,  selection = .mean(-12:2) 
                       + .mean(3:5) + .mean(6:8) + .mean (9:11) + .mean (-9:-11), 
                       method = "correlation",
                       dynamic = "static", win_size = 25, win_offset = 1,
                       start_last = TRUE, var_names = NULL, ci = 0.05,
                       boot = "std", sb = TRUE)

plot(vt.h.e.nadp5) 
coef(vt.h.e.nadp5) #NS

##CO2
choose.files()
quru.co2.high_elev  <- read.csv("C:\\Users\\Rebecca Stern\\Documents\\UVM\\Research\\QURU 2015-16\\Excel Files\\RW\\co2_high_elev_quru.csv")
head(quru.co2.high_elev)

qx <- quru.co2.high_elev$mean_high
qy <- quru.co2.high_elev$mean_CO2

#Correlation:
cor.test(qx,qy, method = "pearson", data=quru.co2.high_elev, na.omit=TRUE) #ns, results below
```

Pearson's product-moment correlation

data:  qx and qy
t = 0.11405, df = 78, p-value = 0.9095
alternative hypothesis: true correlation is not equal to 0
95 percent confidence interval:
 -0.2073929  0.2319711
sample estimates:
       cor 
0.01291235 