---
title: "QURU_dome1_ew"
author: "R Stern"
date: "March 20,2018"
output: html_document
---
```{r}
library(graphics)
library(stats)
library(utils)
library(dplR)
library(ggplot2)
library(dplyr)

choose.files()

dome1.ew <- read.tucson("C:\\Users\\Rebecca Stern\\Documents\\UVM\\Research\\QURU 2015-16\\QURU Sites\\Dome1\\QURU_DOME1_EARLYWOOD.lwr")
head(dome1.ew)
tail(dome1.ew)

#average multiple cores of same tree. first, try autoread.ids(file.rwl). If that doesn't work, then try stc.
dome1.ids.percore <- read.ids(dome1.ew, stc = c(0,4,1))
dome1.ids.percore

dome1.treeMean.ew <- treeMean(dome1.ew, dome1.ids.percore, na.rm=TRUE)
tail(dome1.treeMean.ew)

#to find out how many trees are at this site:
ncol(dome1.treeMean.ew)

#For some reason, 2016 is listed, but we cored in 2015. So, remove 2016:
dome1.treeMean.ew <- dome1.treeMean.ew[ !(rownames(dome1.treeMean.ew) %in% 2016), ]

tail(dome1.treeMean.ew)
```

summary statistics
```{r}
#conduct summary statistics on RRW per tree (treeMean)
dome1.treeMean.ew.sum <- summary(dome1.treeMean.ew)

#to get mean EW, SD for EW:
mean(dome1.treeMean.ew.sum$mean)
mean(dome1.treeMean.ew.sum$year)
min(dome1.treeMean.ew.sum$first)
max(dome1.treeMean.ew.sum$last)
mean(dome1.treeMean.ew.sum$stdev)
mean(dome1.treeMean.ew.sum$median)
mean(dome1.treeMean.ew.sum$ar1)

#average mean sensitivity- there are two measures of sensitivity here (sens1 and sens2).I used sens2. See word doc titled "notes and ideas for red oak manuscript" for more info. In this case, they are basically the same anyway.
mean(dome1.treeMean.ew.sum$sens1) #0.130
mean(dome1.treeMean.ew.sum$sens2) #0.128

#to get mean interseries correlation or original RRW rwl
mean(interseries.cor(dome1.ew)[, 1])

plot(dome1.treeMean.ew, plot.type="spag")

```

Detrend with a spline
```{r}
dome1.ew.spline <- detrend(rwl = dome1.treeMean.ew, method = "Spline")
tail(dome1.ew.spline)

library(doParallel)

#check stats/EPS of spline method
#read in ids based on treeMean
dome1.ids.treeMean.ew <- read.ids(dome1.treeMean.ew,stc = c(0,4,1))
head( dome1.ids.treeMean.ew)

dome1.stats.ew.spline <- rwi.stats.running(dome1.ew.spline, 
                                           dome1.ids.treeMean.ew,
                                            window.length = 20)
dome1.stats.ew.spline 

```

Create site chronology with spline (default spline settings):
```{r}
dome1.ew.spline.crn <- chron(dome1.ew.spline, prefix = "DO1", 
                          biweight = TRUE, 
                          prewhiten = TRUE)
head(dome1.ew.spline.crn)
tail(dome1.ew.spline.crn)

#truncate based on EPS, which for this site was the year 1925:
nrow(dome1.ew.spline.crn)

dome1.ew.spline.tcrn <- dome1.ew.spline.crn [51:141,]
head(dome1.ew.spline.tcrn)
tail(dome1.ew.spline.tcrn)

par(mfrow=c(1,1))

plot(dome1.ew.spline.tcrn,xlab="Year",ylab="RWI") #standardized chronology on top, residual chronology on bottom. Sample depth is trees, not cores.

#remove the standardized chronology to prep for creating CSV
dome1.ew.spline.tcrn <-dome1.ew.spline.tcrn[-1]
dome1.ew.spline.tcrn <- cbind(rownames(dome1.ew.spline.tcrn), dome1.ew.spline.tcrn)
rownames(dome1.ew.spline.tcrn) <- NULL
colnames(dome1.ew.spline.tcrn) <- c("year","dome1_ewres","dome1.s.dep")
head(dome1.ew.spline.tcrn)
tail(dome1.ew.spline.tcrn)

#create CSV file for future reference (so don't have to re-run code every time)
write.csv(dome1.ew.spline.tcrn, "C:\\Users\\Rebecca Stern\\Documents\\UVM\\Research\\QURU 2015-16\\QURU Sites\\Dome1\\Residual chronologies\\QURU_dome1_ew_defspline_trunc.csv", row.names=FALSE)
```

Detrend using 20-year spline:
```{r}
dome1.ew.spline.20 <-detrend(dome1.treeMean.ew, y.name = names(dome1.treeMean.ew),                make.plot = FALSE, 
               method = "Spline",
               nyrs = 20, f = 0.5,
               verbose = FALSE, return.info = FALSE, span = "cv", bass = 0)

#check stats/EPS of 20-yr spline 
dome1.ew.spline.20.stats  <- rwi.stats.running(dome1.ew.spline.20,
                                                dome1.ids.treeMean.ew,
                                               window.length = 20)
dome1.ew.spline.20.stats
```

Create site chronology with 20-year spline:
```{r}
dome1.ew.spline.20.crn <- chron(dome1.ew.spline.20, prefix = "DO1", 
                          biweight = TRUE, 
                          prewhiten = TRUE)
head(dome1.ew.spline.20.crn)
tail(dome1.ew.spline.20.crn)

#truncate based on EPS, which for this site was the year 1925:
nrow(dome1.ew.spline.20.crn)

dome1.ew.spline.20.tcrn <- dome1.ew.spline.20.crn [51:141,]
head(dome1.ew.spline.20.tcrn)
tail(dome1.ew.spline.20.tcrn)

par(mfrow=c(1,1))

plot(dome1.ew.spline.20.tcrn,xlab="Year",ylab="RWI") #standardized chronology on top, residual chronology on bottom. Sample depth is trees, not cores.

#remove the standardized chronology to prep for creating CSV
dome1.ew.spline.20.tcrn <-dome1.ew.spline.20.tcrn[-1]
dome1.ew.spline.20.tcrn <- cbind(rownames(dome1.ew.spline.20.tcrn), dome1.ew.spline.20.tcrn)
rownames(dome1.ew.spline.20.tcrn) <- NULL
colnames(dome1.ew.spline.20.tcrn) <- c("year","dome1_ewres","dome1.s.dep")
head(dome1.ew.spline.20.tcrn)
tail(dome1.ew.spline.20.tcrn)

#create CSV file for future reference (so don't have to re-run code every time)
write.csv(dome1.ew.spline.20.tcrn, "C:\\Users\\Rebecca Stern\\Documents\\UVM\\Research\\QURU 2015-16\\QURU Sites\\Dome1\\Residual chronologies\\QURU_dome1_ew_20spline_trunc.csv", row.names=FALSE)

```

Detrend using a 30 year spline
```{r}
dome1.ew.spline.30 <- detrend(dome1.treeMean.ew, y.name = names(dome1.treeMean.ew),                              make.plot = FALSE, 
                             method = "Spline",
                             nyrs = 30, f = 0.5,
                             verbose = FALSE, return.info = FALSE, span = "cv",
                             bass = 0)

#check stats/EPS of 30-yr spline 
dome1.ew.spline.30.stats  <- rwi.stats.running(dome1.ew.spline.30,
                                               dome1.ids.treeMean.ew,
                                               window.length = 20)
dome1.ew.spline.30.stats
```

Create site chronology with 30-year spline:
```{r}
dome1.ew.spline.30.crn <- chron(dome1.ew.spline.30, prefix = "DO1", 
                          biweight = TRUE, 
                          prewhiten = TRUE)
head(dome1.ew.spline.30.crn)
tail(dome1.ew.spline.30.crn)

#truncate based on EPS, which for this site was the year 1925:
nrow(dome1.ew.spline.30.crn)

dome1.ew.spline.30.tcrn <- dome1.ew.spline.30.crn [51:141,]
head(dome1.ew.spline.30.tcrn)
tail(dome1.ew.spline.30.tcrn)

par(mfrow=c(1,1))

plot(dome1.ew.spline.30.tcrn,xlab="Year",ylab="RWI") #standardized chronology on top, residual chronology on bottom. Sample depth is trees, not cores.

#remove the standardized chronology to prep for creating CSV
dome1.ew.spline.30.tcrn <-dome1.ew.spline.30.tcrn[-1]
dome1.ew.spline.30.tcrn <- cbind(rownames(dome1.ew.spline.30.tcrn), dome1.ew.spline.30.tcrn)
rownames(dome1.ew.spline.30.tcrn) <- NULL
colnames(dome1.ew.spline.30.tcrn) <- c("year","dome1_ewres","dome1.s.dep")
head(dome1.ew.spline.30.tcrn)
tail(dome1.ew.spline.30.tcrn)

#create CSV file for future reference (so don't have to re-run code every time)
write.csv(dome1.ew.spline.30.tcrn, "C:\\Users\\Rebecca Stern\\Documents\\UVM\\Research\\QURU 2015-16\\QURU Sites\\Dome1\\Residual chronologies\\QURU_dome1_ew_30spline_trunc.csv", row.names=FALSE)
```

Detrend using a 40 year spline
```{r}
dome1.ew.spline.40 <- detrend(dome1.treeMean.ew, y.name = names(dome1.treeMean.ew),
                              make.plot = FALSE, 
                              method = "Spline",
                              nyrs = 40, f = 0.5,
                              verbose = FALSE, return.info = FALSE, span = "cv",
                              bass = 0)

#check stats/EPS of 40-yr spline 
dome1.ew.spline.40.stats  <- rwi.stats.running(dome1.ew.spline.40,
                                               dome1.ids.treeMean.ew,
                                               window.length = 20)
dome1.ew.spline.40.stats
```


Create site chronology with 40-year spline:
```{r}
dome1.ew.spline.40.crn <- chron(dome1.ew.spline.40, prefix = "DO1", 
                          biweight = TRUE, 
                          prewhiten = TRUE)
head(dome1.ew.spline.40.crn)
tail(dome1.ew.spline.40.crn)

#truncate based on EPS, 1925:
nrow(dome1.ew.spline.40.crn)

dome1.ew.spline.40.tcrn <- dome1.ew.spline.40.crn [51:141,]
head(dome1.ew.spline.40.tcrn)
tail(dome1.ew.spline.40.tcrn)

par(mfrow=c(1,1))

plot(dome1.ew.spline.40.tcrn,xlab="Year",ylab="RWI") #standardized chronology on top, residual chronology on bottom. Sample depth is trees, not cores.

#remove the standardized chronology to prep for creating CSV
dome1.ew.spline.40.tcrn <-dome1.ew.spline.40.tcrn[-1]
dome1.ew.spline.40.tcrn <- cbind(rownames(dome1.ew.spline.40.tcrn), dome1.ew.spline.40.tcrn)
rownames(dome1.ew.spline.40.tcrn) <- NULL
colnames(dome1.ew.spline.40.tcrn) <- c("year","dome1_ewres","dome1.s.dep")
head(dome1.ew.spline.40.tcrn)
tail(dome1.ew.spline.40.tcrn)

#create CSV file for future reference (so don't have to re-run code every time)
write.csv(dome1.ew.spline.40.tcrn, "C:\\Users\\Rebecca Stern\\Documents\\UVM\\Research\\QURU 2015-16\\QURU Sites\\Dome1\\Residual chronologies\\QURU_dome1_ew_40spline_trunc.csv", row.names=FALSE)
```

Detrend using a 50 year spline
```{r}
dome1.ew.spline.50 <- detrend(dome1.treeMean.ew, y.name = names(dome1.treeMean.ew),
                              make.plot = FALSE, 
                              method = "Spline",
                              nyrs = 50, f = 0.5,
                              verbose = FALSE, return.info = FALSE, span = "cv",
                              bass = 0)

#check stats/EPS of 50-yr spline 
dome1.ew.spline.50.stats  <- rwi.stats.running(dome1.ew.spline.50,
                                               dome1.ids.treeMean.ew,
                                               window.length = 20)
dome1.ew.spline.50.stats
```

Create site chronology with 50-year spline:
```{r}
dome1.ew.spline.50.crn <- chron(dome1.ew.spline.50, prefix = "DO1", 
                          biweight = TRUE, 
                          prewhiten = TRUE)
head(dome1.ew.spline.50.crn)
tail(dome1.ew.spline.50.crn)

#truncate based on EPS, 1925:
nrow(dome1.ew.spline.50.crn)

dome1.ew.spline.50.tcrn <- dome1.ew.spline.50.crn [51:141,]
head(dome1.ew.spline.50.tcrn)
tail(dome1.ew.spline.50.tcrn)

par(mfrow=c(1,1))

plot(dome1.ew.spline.50.tcrn,xlab="Year",ylab="RWI") #standardized chronology on top, residual chronology on bottom. Sample depth is trees, not cores.

#remove the standardized chronology to prep for creating CSV
dome1.ew.spline.50.tcrn <-dome1.ew.spline.50.tcrn[-1]
dome1.ew.spline.50.tcrn <- cbind(rownames(dome1.ew.spline.50.tcrn), dome1.ew.spline.50.tcrn)
rownames(dome1.ew.spline.50.tcrn) <- NULL
colnames(dome1.ew.spline.50.tcrn) <- c("year","dome1_ewres","dome1.s.dep")
head(dome1.ew.spline.50.tcrn)
tail(dome1.ew.spline.50.tcrn)

#create CSV file for future reference (so don't have to re-run code every time)
write.csv(dome1.ew.spline.50.tcrn, "C:\\Users\\Rebecca Stern\\Documents\\UVM\\Research\\QURU 2015-16\\QURU Sites\\Dome1\\Residual chronologies\\QURU_dome1_ew_50spline_trunc.csv", row.names=FALSE)
```

Detrend using FSS
```{r}
#detrend using FSS
dome1.ew.fss <- detrend(rwl = dome1.treeMean.ew, method = "Friedman")
tail(dome1.ew.fss)

#check stats/EPS of FSS method
#read in ids based on treeMean
dome1.ids.treeMean <- read.ids(dome1.treeMean.ew,stc = c(0,4,1))
head(dome1.ids.treeMean)

dome1.stats.ew.fss <- rwi.stats.running(dome1.ew.fss, dome1.ids.treeMean.ew,
                                            window.length = 20)

dome1.stats.ew.fss 
```

Create site chronology with FSS:
```{r}
dome1.ew.fss.crn <- chron(dome1.ew.fss, prefix = "DO1", 
                          biweight = TRUE, 
                          prewhiten = TRUE)
head(dome1.ew.fss.crn)
tail(dome1.ew.fss.crn)

#truncate based on EPS, which for this site was the year 1925:
nrow(dome1.ew.fss.crn)

dome1.ew.fss.tcrn <- dome1.ew.fss.crn [51:141,]
head(dome1.ew.fss.tcrn)
tail(dome1.ew.fss.tcrn)

par(mfrow=c(1,1))

plot(dome1.ew.fss.tcrn,xlab="Year",ylab="RWI") #standardized chronology on top, residual chronology on bottom. Sample depth is trees, not cores.

#remove the standardized chronology to prep for creating CSV
dome1.ew.fss.tcrn <-dome1.ew.fss.tcrn[-1]
dome1.ew.fss.tcrn <- cbind(rownames(dome1.ew.fss.tcrn), dome1.ew.fss.tcrn)
rownames(dome1.ew.fss.tcrn) <- NULL
colnames(dome1.ew.fss.tcrn) <- c("year","dome1_ewres","dome1.s.dep")
head(dome1.ew.fss.tcrn)
tail(dome1.ew.fss.tcrn)

#create CSV file for future reference (so don't have to re-run code every time)
write.csv(dome1.ew.fss.tcrn, "C:\\Users\\Rebecca Stern\\Documents\\UVM\\Research\\QURU 2015-16\\QURU Sites\\Dome1\\Residual chronologies\\dome1_ew_fss_trunc.csv", row.names=FALSE)
```


